---
title: 'Summary of the Models: Intonation and perlocution'
author: "Sunwoo Jeong"
date: "February 15, 2016"
fontsize: 11pt
geometry: margin=0.8in
output: 
  pdf_document:
    keep_tex: yes
---

A combined data set from the polar interrogative-experiment (experiment 1) and the wh-interrogative / imperative / declarative experiment (experiment 2) has been created.

The data frame (dat1) contains all the data from experiment 2, as well as from experiment 3, as long as the data are from stimuli manipulated in intonation.

```{r}
### Load the combined data
setwd("/Users/sunwoojeong/Desktop/perlocution_experiment/")
dat1 <- read.csv('perlocution_combined_data_exp1_exp2.csv')
```

```{r, echo=FALSE}
# Recode HRise as Rise, because they are the same
dat1$intonation <- as.character(dat1$intonation)
dat1$intonation[dat1$intonation == "H_rise"] <- "Rise"
dat1$intonation <- as.factor(dat1$intonation)

dat1 <- dat1[dat1$intonation != 'H_Level', ]
dat1 <- dat1[dat1$intonation != 'L_rise', ]
```

Setting the most widely applicable default baselines for each predictors.
```{r, echo=FALSE}
library(lmerTest)
library(texreg)
```
```{r}
dat1$intonation <- relevel(dat1$intonation, 'Fall')
dat1$illocution <- relevel(dat1$illocution, 'request')
dat1$sentence_type <- relevel (dat1$sentence_type, 'polar_Q')
```

# Annoyance rating 
**(base: polar-Q, request illocution, Falling intonation)**

The model for the annoyance rating is as follows:
```{r}
m1 <- lmer(annoyance ~ intonation * illocution * sentence_type + (1|speaker) + (1|subject), data = dat1)
summary(m1)
screenreg(m1)

# Different baselines could be set for different sentence types

dat1$sentence_type <- relevel (dat1$sentence_type, 'Wh_Q')
dat1$sentence_type <- relevel (dat1$sentence_type, 'Declarative')
dat1$sentence_type <- relevel (dat1$sentence_type, 'Imperative')
dat1$sentence_type <- relevel (dat1$sentence_type, 'polar_Q')
```

**Notes on the main predictors**

**Intonation**: For polar interrogatives, **annoyance is signalled by: Level > Fall > Rise**.

**Illocution**: If the (polar interrogative) utterance is perceived as **request or accusation** illocutions, the speaker is taken to be significantly **more annoyed** than if the utterance is perceived as information seeking (p < .001 for both).

**Sentence-type**: **Wh-interrogatives** elicit significantly **higher annoyance ratings** (p < .001) than polar interrogatives, overall.

There are significant interactions between intonation, illocution, and sentence type as well. To mention just a few important ones:

**Notes on the two-way interactions**

1. Level contour, when combined with request illocution (all sentence types) or suggestion illocution (imperatives), boosts the annoyance rating (sounds more annoyed).

2. Rising contour occuring with wh-interrogatives boosts the annoyance rating. **This basically means that there's less difference between rising and falling contours for wh-interrogatives in signalling annoyance, than the difference between rising and falling contours for polar-interrogatives.**

3. Invitation illocution occuring with declaratives or with wh-interrogatives lowers the annoyance rating.

**Notes on the three-way interactions**

4. (High) Rising intonation in declaratives and wh-interrogatives, if perceived to be invitations, signal significantly more annoyance. **This basically means that the above-mentioned reduction in gap between rising and falling contours for wh-interrogatives is even stronger when the illocution is taken to be invitation.**


# Authority rating 
**(base: polar-Q, request illocution, Falling intonation)**

The model for the annoyance rating is as follows:
```{r}
m2 <- lmer(authority ~ intonation * illocution * sentence_type + (1|speaker) + (1|subject), data = dat1)
summary(m2)
screenreg(m2)

# Relevel intonation to enable 3-way comparison between them

dat1$intonation <- relevel(dat1$intonation, 'Level')
m2_2 <- lmer(authority ~ intonation * illocution * sentence_type + (1|speaker) + (1|subject), data = dat1)
summary(m2_2)
screenreg(m2_2)

dat1$intonation <- relevel(dat1$intonation, 'Fall')
```

**Notes on the main predictors**

**Intonation**: For polar interrogatives, authority is signalled by: **Fall > Level > Rise**.

**Illocution**: Again, if the utterance is perceived as **request or accusation** illocutions, the speaker is taken to be significantly **more authoritative** than if the utterance is perceived as information seeking (p < .001 for both).

**Sentence-type**: Again, **wh-interrogatives** elicit significantly **higher authority** ratings (p < .001).

**Notes on the two-way interactions**

1. Rising contour, when combined with the declarative sentence type, lowers the authority ratings (specifically for info_s illocutions).

2. Request illocution, when conveyed by the declarative sentence type, signal significantly more authority than when conveyed by other sentence types.


# Politeness rating 
**(base: polar-Q, request illocution, Falling intonation)**

Model for the politeness rating are as follows:
```{r}
m3 <- lmer(polite ~ intonation * illocution * sentence_type + (1|speaker) + (1|subject), data = dat1)
summary(m3)
screenreg(m3)
```

**Notes on the main predictors**

**Intonation**: For polar interrogatives, politeness is signalled by: **Rise > Level, Fall**.

**Illocution**: If the utterance is perceived as **request or accusation** illocutions, the speaker is taken to be significantly **less polite** than if the utterance is perceived as information seeking (p < .001 for both).

**Sentence-type**: **Wh-interrogatives** elicit significantly **lower politeness** ratings (p < .001).

**Notes on the two-way interactions**

1. Rises in wh-interrogatives signal less politeness. **Again, this basically means that there's less difference between rising and falling contours for wh-interrogatives in signalling politeness, than the difference between rising and falling contours for polar-interrogatives.**

2. Invitation and requests in wh-interrogatives boosts the politeness rating.

**Notes on the three-way interactions**

3. But rising invitations in wh-interrogatives lowers the politeness rating.


# Stance rating 
**(base: polar-Q, request illocution, Falling intonation)**

Model for the stance rating are as follows:
```{r}
m4 <- lmer(stance ~ intonation * illocution * sentence_type + (1|speaker) + (1|subject), data = dat1)
summary(m4)
screenreg(m4)
```

**Intonation**: For polar interrogatives, positive stance is signalled by: **Rise > Level, Fall**.

**Illocution**: If the utterance is perceived as **accusation** illocutions, the speaker is taken to signal significantly more **negative stance** than if the utterance is perceived as information seeking (p < .001).

**Sentence-type**: **Wh-interrogatives** elicit significantly **lower stance** ratings (p < .001).

**Notes on the two-way interactions**

1. Rising intonation combined with invitation illocution boosts the positive stance rating.

2. Rises in wh-interrogatives signal less positive stance. **Again, this basically means that there's less difference between rising and falling contours for wh-interrogatives in signalling positive stance, than the difference between rising and falling contours for polar-interrogatives.**

3. Invitation illocution conveyed by wh-interrogatives boosts positive stance rating.

